Comparison of Terrain Following and Cut Cell Grids with a Non-Hydrostatic Model

### 2015-02-18 msc-publication.tex
describe projection method for divergence free velocity field

\TODO{define the continuous wind profile, say that wind is prescribed at cell faces, and explain how we make it discretely non-divergent}

@@

%The tracer is positioned such that it is centred above the mountain at \(t = \SI{5000}{\second}\).

Unlike \citet{schaer2002} who use periodic lateral boundaries, we use a fixed value of 0 at the inlet boundary and zero gradient boundaries elsewhere.
Tests are integrated forward in time for \SI{10000}{\second} with a timestep of \(\Delta t = \SI{25}{\second}\).

@@

@@

\begin{table}[t]
\caption{Min, max and error norms compared with \citet{schaer2002}}
\label{tab:advection}
%
\begin{center}
\begin{tabular}{ l l l l l l }
\hline\hline
& \multicolumn{3}{c}{Cubic upwind-biased} & \multicolumn{2}{c}{Sch\"ar 4th order} \\
& \(\ell^2\) error & min & max & min & max \\
\hline
Analytic  & 0 & 0 & 1 & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\
BTF 	  & TODO & TODO & TODO & \num{-0.058} & \num{1.001} \\
SLEVE 	  & TODO & TODO & TODO & TODO & TODO \\
SnapCol   & TODO & TODO & TODO & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\
noOrography & TODO & TODO & TODO & \num{-0.002} & \num{0.984} \\
\hline
\end{tabular}
\end{center}
\end{table}

>>>>

While the continuous wind field specified by \citet{schaer2002} is non-divergent, this is not true of the discrete wind field on non-orthogonal grids.  A potential, $p$, is used to correct the wind field, $\bm{u}$, so that is non-divergent such that
\begin{align}
	\nabla \cdot \left( \bm{u} + \nabla p \right) = 0,
\intertext{which can be rearranged to give a Poisson equation}
	\nabla^2 p = - \nabla \cdot \bm{u}.
\end{align}

@@

Unlike \citet{schaer2002} who use periodic lateral boundaries, a fixed value of 0 is used at the inlet boundary and all other boundaries have zero gradient.
Tests are integrated forward in time for \SI{10000}{\second} with a timestep of \(\Delta t = \SI{25}{\second}\).

@@

\begin{table}[t]
\caption{Min, max and error norms compared with \citet{schaer2002}}
\label{tab:advection}
%
\centering
\footnotesize
\begin{tabular}{ l l l l l l }
\hline\hline
& \multicolumn{3}{c}{Cubic upwind-biased} & \multicolumn{2}{c}{Sch\"ar 4th order} \\
& \(\ell^2\) error & min & max & min & max \\
\hline
Analytic  & 0 & 0 & 1 & 0 & 1 \\
BTF 	  & \num{0.00758} & \num{-0.034} & \num{0.928} & \num{-0.058} & \num{1.001} \\
SLEVE 	  & \num{0.00110} & \num{-0.011} & \num{0.981} & \num{-0.002} & \num{0.984} \\
SnapCol   & \num{0.00058} & \num{-0.007} & \num{0.982} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\
noOrography & \num{0.00058} & \num{-0.007} & \num{0.982} & \num{-0.002} & \num{0.984} \\
\hline
\end{tabular}
\end{table}

@@
